The SMT Competition 2015--2018

### 2019-08-27 2018/report/SMT-COMP.tex
Institutional affiliations are optional

Tables~\ref{table:participants1}--\ref{table:participants3} list the solvers
that participated between~2015 and~2018, together with contributing team
members (in alphabetical order) and their institutional affiliations (which may
have changed over time) as reported by the development teams.

>>>>

Tables~\ref{table:participants1}--\ref{table:participants3} list the
solvers that participated between~2015 and~2018, together with
contributing team members (in alphabetical order) and their
institutional affiliations (if any; these may have changed over time)
as reported by the development teams.
